GA-based Training-Free NAS Algorithm with Hybrid Score Function

### 2023-03-05 paper/main.tex
update

    To overcome this challenge, recent works developed and proposed lots 
    of method which is so called training-free NAS. Some use mean absolute 
    error random sampling (MRS) (Camero et al.,\ \cite{https://doi.org/10.48550/arxiv.1805.07159}, 
    Camero et al.,\ \cite{Camero_2021}, Camero et al.,\ \cite{https://doi.org/10.48550/arxiv.2106.15295}) 
    as a training-free score function and some use neural tangent kernel 
    (NTK) (Chen et al.,\ \cite{https://doi.org/10.48550/arxiv.2102.11535}, 
    Wang et al.,\ \cite{https://doi.org/10.48550/arxiv.2203.09137}, 
    Shu et al.,\ \cite{https://doi.org/10.48550/arxiv.2109.00817}), while 
    some use gradient-based methods (Zhang \& Jia,\ \cite{https://doi.org/10.48550/arxiv.2110.08616}, 
    Cavagnero et al.,\ \cite{https://doi.org/10.48550/arxiv.2207.05135}, 
    Abdelfattah et al.,\ \cite{https://doi.org/10.48550/arxiv.2101.08134}).
% what is unknown?
    However, most of score functions suffer from low correlation between 
    score value and the result of an architecture, leading to a trap that 
    no matter how good the search method is used, we can hardly find an 
    optimal architecture.
% how and why
    The major problem causes the low correlation is that a single score 
    function can only evaluate one perspect/characteristic of an architecture.
% method
    By cooperating three heterogeneous score functions with genetic-based 
    search method, we shall evaulate an architecture from different aspects. 
    More specifically, the first score function is noise immunity for neural 
    architecture search without search (NINASWOT) (Wu et al.\ \cite{10.1145/3491396.3506510}). 
    Based on the work of Mellor et al., they proposed the measurement of 
    the correlation between binary activation paterns of input data at each 
    ReLU layer. Later, Wu et al. found a high score obtained by such a 
    function may not correspond to a high-performence model. Thus, they 
    additionally applied noisy immunity method, called NINASWOT. Second one 
    is maximum-entropy detection (MAE-DET) (Sun et al.\ \cite{https://doi.org/10.48550/arxiv.2111.13336}). 
    Based on the work of Sun et al., they proposed to find the maximum of 
    the differential entropy by calculating the variance of the output at 
    the final layer with the input Gaussian noise images. Third one is 
    condition number of  neural tangent kernel (NTK) (Chen et al.\ \cite{https://doi.org/10.48550/arxiv.2102.11535}), 
    which is defined as 
    \begin{equation}
        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
    \end{equation}
    Chen et al. used the condition number of NTK as the score function to estimate the performance of a network.
% results
    It's shall find good architectures in reasonable time and computational resource.
% conclusion
    The major contribution of this paper can be summarized as follow:
    \begin{itemize}
        \item 
    \end{itemize}

    The remainder of this paper is organized as follows:

>>>>

    To overcome this challenge, recent works developed and proposed lots 
    of method which is so called training-free NAS. Some use mean absolute 
    error random sampling (MRS) (Camero et al.,\ \cite{https://doi.org/10.48550/arxiv.1805.07159}, 
    Camero et al.,\ \cite{Camero_2021}, Camero et al.,\ \cite{https://doi.org/10.48550/arxiv.2106.15295}) 
    as a training-free score function and some use neural tangent kernel 
    (NTK) (Chen et al.,\ \cite{https://doi.org/10.48550/arxiv.2102.11535}, 
    Wang et al.,\ \cite{https://doi.org/10.48550/arxiv.2203.09137}, 
    Shu et al.,\ \cite{https://doi.org/10.48550/arxiv.2109.00817}), while 
    some use gradient-based methods (Zhang \& Jia,\ \cite{https://doi.org/10.48550/arxiv.2110.08616}, 
    Cavagnero et al.,\ \cite{https://doi.org/10.48550/arxiv.2207.05135}, 
    Abdelfattah et al.,\ \cite{https://doi.org/10.48550/arxiv.2101.08134}).
% what is unknown?
    However, most of score functions suffer from low correlation between 
    score value and the result of an architecture, leading to a trap that 
    no matter how good the search method is used, we can hardly find an 
    optimal architecture.
% how and why
    The major problem causes the low correlation is that a single score 
    function can only evaluate one perspect/characteristic of an architecture.
% method
    By cooperating three heterogeneous score functions with genetic-based 
    search method, we shall evaulate an architecture from different aspects. 
    More specifically, the first score function is noise immunity for neural 
    architecture search without search (NINASWOT) (Wu et al.\ \cite{10.1145/3491396.3506510}). 
    Based on the work of Mellor et al., they proposed the measurement of 
    the correlation between binary activation paterns of input data at each 
    ReLU layer. Later, Wu et al. found a high score obtained by such a 
    function may not correspond to a high-performence model. Thus, they 
    additionally applied noisy immunity method, called NINASWOT. Second one 
    is maximum-entropy detection (MAE-DET) (Sun et al.\ \cite{https://doi.org/10.48550/arxiv.2111.13336}). 
    Based on the work of Sun et al., they proposed to find the maximum of 
    the differential entropy by calculating the variance of the output at 
    the final layer with the input Gaussian noise images. Third one is 
    condition number of  neural tangent kernel (NTK) (Chen et al.\ \cite{https://doi.org/10.48550/arxiv.2102.11535}), 
    which is defined as 
    \begin{equation}
        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
    \end{equation}
    Chen et al. used the condition number of NTK as the score function to 
    estimate the performance of a network.
% results
    It's shall find good architectures in reasonable time and computational 
    resource.
% conclusion
    The major contribution of this paper can be summarized as follow:
    \begin{itemize}
        \item Use hybrid score functions method to predict the performance 
        of an architecture
        \item 
        \item The simulation results show that 
    \end{itemize}

    The remainder of this paper is organized as follows: Section 2 provides a 
    brief introduction to state-of-the-art NAS techniques and describe the 
    method in detail. Section 3 gives a detailed descriptions of the proposed 
    method. Section 4 provides the results of the simulation.
